Visit Scotland Notebook

### 2023-06-16 visit_scotland_notebook.Rmd
Updated Summary Stats for Domestic and International

```{r}
library(tidyverse)
library(here)
library(sf)
library(infer)
library(ggridges)
library(modelr)
```

@@

@@

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = visits)) +
  geom_line(group = 1, size = 1, colour = "#540453") +
  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
  labs(x = "\n Year Range",
       y = "Visitors (Thousands) \n",
       title = "Average Annual Number of Domestic Vistors",
       subtitle = "3 Year Average") +
  ylim(0, 13000)

@@

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = expenditure)) +
  geom_line(group = 1, size = 1, colour = "#540453") +
  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
  labs(x = "\n Year Range",
       y = "Expenditure (Million GBP) \n",
       title = "Average Annual Expenditure of Domestic Vistors",
       subtitle = "3 Year Average") +
  ylim(0, 3500)

@@

### Visit Stats

```{r}
international_visits %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
  group_by(year) %>% 
  summarise(sum_annual_visits = sum(visits)) %>% 
  summarise(avg_annual_visits = mean(sum_annual_visits))

@@

```{r}
international_visits %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
  group_by(year) %>% 
  summarise(sum_annual_exp = sum(spend)) %>% 
  summarise(avg_annual_spend = mean(sum_annual_exp))

>>>>

```{r}
library(tidyverse)
library(here)
library(sf)
library(infer)
library(ggridges)
library(modelr)
library(skimr)
```

@@

## Annual Average Stats

#### 5 Figure Summary

```{r}
regional_domestic_tourism_all %>% 
  skim()
```

#### IQR

```{r}
regional_domestic_tourism_all %>% 
  summarise(visits_iqr= IQR(visits),
            expenditure_iqr= IQR(expenditure))
```

#### Median

```{r}
regional_domestic_tourism_all %>% 
  summarise(median_visits = median(visits),
            median_expenditure = median(expenditure))

### Annual Average Boxplots

```{r}
regional_domestic_tourism_all %>% 
  ggplot(aes(x = visits, y = region_of_residence)) +
  geom_boxplot(fill = "#540453", alpha = 0.5) +
  stat_summary(fun.y = mean, geom = "point", shape = 4, size = 5, color = "#1d1d65", fill="#1d1d65") +
  labs(
    title = "Distribution of Annual Number of Domestic Vistors",
    x = "Visits (Thousands)",
    y = "Region of Residence",
    subtitle = "3 Year Averages")
```

```{r}
regional_domestic_tourism_all %>% 
  ggplot(aes(x = expenditure, y = region_of_residence)) +
  geom_boxplot(fill = "#1d1d65", alpha = 0.5) +
  stat_summary(fun.y = mean, geom = "point", shape = 4, size = 5, color="#540453", fill="#540453") +
  labs(
    title = "Distribution of Average Annual Expenditure of Domestic Vistors",
    x = "Expenditure (Million GBP)",
    y = "Region of Residence",
    subtitle = "3 Year Averages")
```

@@

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = visits)) +
  geom_line(group = 1, size = 1, colour = "#540453") +
  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
  labs(x = "\n Year Range",
       y = "Visitors (Thousands) \n",
       title = "Average Annual Number of Domestic Vistors",
       subtitle = "3 Year Averages") +
  ylim(0, 13000)

@@

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = expenditure)) +
  geom_line(group = 1, size = 1, colour = "#540453") +
  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
  labs(x = "\n Year Range",
       y = "Expenditure (Million GBP) \n",
       title = "Average Annual Expenditure of Domestic Vistors",
       subtitle = "3 Year Averages") +
  ylim(0, 3500)

@@

### Annual Average Stats

#### Mean

```{r}
international_visits %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
  group_by(year) %>% 
  summarise(sum_annual_visits = sum(visits),
            sum_annual_spend = sum(spend)) %>%
  summarise(mean_annual_visits = mean(sum_annual_visits),
            mean_annual_spend = mean(sum_annual_spend))
```

@@
